### 2019-12-15 ic-journal/sos.tex
text

The CCS formalisation starts with type definitions for action,
relabeling and then the  processes. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
to $\mathscr{L}$ (the set of names for labels) \hl{mentioned} at the beginning
of Section~\ref{ss:ccs}. (Thus the
cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' depend on \hl{its type variable:
\mbox{when $\beta$ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is countable.}})
All labels are divided into input and output ones.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
following syntax:
\begin{lstlisting}
Datatype: Label = name 'b | coname 'b
End
\end{lstlisting}
Intuitively, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' turns names in $\mathscr{L}$ into \emph{input and output labels}.
For instance, if the type $\beta$ is instantiated to \texttt{string}
(the type of all ASCII strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input \emph{label} $a$ and output
\emph{label} $\overline{b}$, respectively.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
union of \hl{all visible actions (input and output labels) and the invisible action} $\tau$
(\texttt{tau}). For instace, the input \emph{action} $a$ and output
\emph{action} $\overline{b}$ of the type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively. \hl{On the
other hand,} \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions of the type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
\HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.

@@

  \item \emph{rules} is a conjunction of implications that will be the
    same as the input term. In fact, the following formal versions of SOS rules are

@@

For instance, \hl{the following proposition
can only be proven by using the above \emph{cases} theorem}:

>>>>

The CCS formalisation starts with type definitions for action,
relabeling and then the  processes. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
to $\mathscr{L}$ (the set of names for labels) \hl{mentioned} at the beginning
of Section~\ref{ss:ccs}. (Thus the
cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''  \hlD{depends on its type variable:
\mbox{when $\beta$ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is countable.}})
All labels are divided into input and output ones.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
following syntax:
\begin{lstlisting}
Datatype: Label = name 'b | coname 'b
End
\end{lstlisting}
Intuitively, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' turns names in $\mathscr{L}$ into \emph{input and output labels}.
For instance, if the type $\beta$ is instantiated to \texttt{string}
(the type of all ASCII strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input \emph{label} $a$ and output
\emph{label} $\overline{b}$, respectively.
The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
union of \hl{all visible actions (input and output labels) and the invisible action} $\tau$
(\texttt{tau}). For instace, the input \emph{action} $a$ and output
\emph{action} $\overline{b}$ of the type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively. \hl{On the
other hand,} \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions of the type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
\HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.

@@

  \item
\emph{rules} is a conjunction of implications (each
    corresponding to a SOS rule) that will be the
    same as the input term.
% \emph{rules} is a conjunction of implications that will be the
%    same as the input term. 
In fact, the following formal versions of SOS rules are

@@

For instance, \hlD{the following proposition
need the above \emph{cases} theorem}:
